Each legal, reachable Tic-Tac-Toe board is represented by
nine values $g_i\in\{-1,0,+1\}$ for circle, empty, and cross.
The three labels are circle win, draw, and cross win, encoded
as $(+1,-1,-1)$, $(-1,+1,-1)$, and $(-1,-1,+1)$. As in
Meyer et al.~\cite{meyer2023symmetry}, unfinished games are
counted as draws. Since the full set contains only 5478 legal,
reachable boards, we enumerate it exactly and draw
class-balanced train and test splits from this set. The labels
are invariant under the eight rotations and reflections of the
board, forming the dihedral group $D_4$; this symmetry is
illustrated in Fig.~\ref{fig:protocol}(a).

We use one qubit per field, as shown in Fig.~\ref{fig:protocol}(b).
Each value $g_i$ is mapped to the angle $x_i=2\pi g_i/3$ and
encoded by an $R_X$ rotation,
\[
U(g)=\bigotimes_{i=0}^{8} R_X\!\left(\frac{2\pi}{3}g_i\right).
\]
The fields are numbered cyclically around the rim, with the
center last. This makes the three $D_4$ position orbits explicit:
corners $\{0,2,4,6\}$, sides $\{1,3,5,7\}$, and center $\{8\}$.

We separate the imposed symmetry from the choice of gates.
Let $H\subseteq D_4$ be the subgroup that we enforce. For
$h\in H$, let $V_h$ act on the board and let $P_h$ be the
corresponding qubit permutation. The encoding is equivariant:
transforming the board before encoding is equivalent to
encoding first and then permuting the qubits,
\[
U(V_h g)=P_h U(g) P_h^\dagger .
\]
A trainable block $W_H(\theta)$ preserves this symmetry if
\[
P_h W_H(\theta) P_h^\dagger = W_H(\theta)
\qquad \text{for all } h\in H .
\]
In practice, we enforce this by sharing parameters across gates
whose supports lie in the same $H$-orbit. For directed gates,
the order of the support is kept fixed, so control and target
roles are not accidentally exchanged. Thus the symmetry fixes
the sharing pattern, but not the gate family itself.

The circuit uses repeated data re-uploading layers. Each layer
applies the encoding $U(g)$ followed by $p$ repetitions of a
trainable block. Unless stated otherwise, we use $L=3$ layers
and $p=2$ repetitions, keeping depth fixed across all sweeps.

Our baseline is the edge ansatz of Meyer et al.,
shown in Fig.~\ref{fig:protocol}(c). It applies local $R_YR_X$
rotations and directed controlled-$R_Y$ entanglers on neighbouring
rim fields and selected center connections. Symmetry enters only
through parameter sharing: gates in the same $H$-orbit share the
same parameter or parameter tuple.

The readout averages Pauli-$Z$ expectations over the three
position orbits,
\[
r_O(g)=\frac{1}{|O|}\sum_{i\in O}\langle Z_i\rangle_g ,
\]
for corners, sides, and center. These three values are used as
class scores. Since the readout orbits are invariant under all
subgroups considered here, the readout is compatible with every
symmetry sweep.

This gives our first design axis: the amount of symmetry imposed.
We keep encoding, edge wiring, gate family, depth, and readout
fixed, and vary only the subgroup $H$. With $r$ denoting a
$90^\circ$ rotation and $f$ a reflection, we compare
$\{e\}$, $\langle r^2\rangle$, $\langle f\rangle$,
$\langle r\rangle=C_4$, $\langle r^2,f\rangle=D_2$, and
$\langle r,f\rangle=D_4$. For the edge ansatz at $L=3,p=2$,
these variants have $204$, $108$, $126$, $60$, $78$, and $54$
trainable parameters, respectively.

The second design axis is the interaction structure. The edge
ansatz couples neighbouring fields, but Tic-Tac-Toe labels are
decided by complete three-cell winning lines. We therefore add
orbit-shared gates on the eight winning triples: three rows,
three columns, and two diagonals, as shown in
Fig.~\ref{fig:protocol}(d). Each triple receives one $ZZZ$ rotation
and one $\mathrm{CCR}_Z$ interaction. The resulting edge+lines
model keeps the original edge ansatz but adds trainable
interactions directly on the label-relevant motifs. At
$L=3,p=2$, the full-$D_4$ edge model has $54$ parameters, while
the full-$D_4$ edge+lines model has $90$.
