The results support a more architectural view of equivariance in variational quantum learning. Meyer et al. showed that enforcing the full task symmetry can improve generalization. Our reproduction confirms that behavior in the same Tic-Tac-Toe setting. But once the model is already equivariant, the remaining design space is still large: one must decide which equivariant interactions are available. The winning-line experiment shows that this choice can matter more than the difference between no symmetry and full symmetry in the original edge ansatz.

This also clarifies what the partial-symmetry experiments do and do not show. They do not establish that $C_4$ is generally better than $D_4$. With five seeds, the honest statement is that $C_4$ is competitive and sometimes slightly ahead, while $D_4$ remains the more conservative default. The value of the partial sweep is that it turns symmetry into a tunable axis and shows that nearby subgroup biases can have similar generalization behavior despite different parameter counts and constraints.

The random-sharing control is essential for the claim. If symmetry-aware tying and random tying performed similarly, then the story would reduce to ordinary regularization by parameter count. They do not. Group-orbit sharing retains substantially more test accuracy than random sharing at the same number of parameters. This supports the interpretation that the circuit benefits from the structure of the board symmetry, not merely from being smaller.

The oracle-inspired ansatz should also be read conservatively. Tic-Tac-Toe is classically solved by a deterministic rule, and our separate rule oracle indeed has zero trainable parameters and perfect accuracy. We do not claim quantum advantage, hardware readiness, or a universal recipe for all symmetric tasks. The claim is narrower and, for that reason, sharper: for a fixed symmetric benchmark and a Meyer-style variational quantum learning setup, task-aligned equivariant gates can substantially improve generalization while preserving the symmetry principle.

The useful analogy is not to a larger neural network that wins by brute force. The edge-plus-line model changes the basis of interactions. The original edge ansatz sees local adjacencies around the board and connections to the center; the winning-line ansatz sees the three-cell motifs from which the label is actually computed. Both are equivariant under the same board group, but they expose different invariant features to the readout. In this sense the result is closer to choosing a convolutional kernel that matches the object geometry than to increasing width.

This distinction matters for future variational quantum learning benchmarks. If a symmetric task has known local motifs, conserved substructures, or relational patterns, then a faithful equivariant circuit should represent those objects directly instead of only tying generic one- and two-qubit gates. The Tic-Tac-Toe case is useful precisely because the correct motifs are obvious: the eight winning lines. That makes the benchmark a controlled demonstration of a broader recipe rather than a hard application.

This makes the result a natural extension of Meyer et al. Their paper asks how to exploit a known symmetry in a variational quantum model. Our answer is that exploiting the symmetry is only the first step. The next step is to design the equivariant gates around the combinatorial structure of the task. In Tic-Tac-Toe, that structure is the set of winning triples. In other domains, it may be local motifs, conserved interaction patterns, or invariant substructures. The broader lesson is that equivariance is not merely a constraint imposed on a generic ansatz; it is a design language for building the ansatz itself.
